MSDS 6372 Project 1 Objective 2

### 2020-02-17 Codebooks/MSDS6372.Project.O2.Rmd
Add files via upload

```{r log tukey pvalues}
#nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
#nyc.anova.log.diff
```

```{r log tukey plot CI}
#plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
```

>>>>

```{r log tukey pvalues}
nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
nyc.anova.log.diff
```

```{r log tukey plot CI}
plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
```
